Open-source landscape for 3D CSEM modelling

### 2020-04-15 manuscript/Manuscript.tex
Include comments Raphael

\tabl[btp]{codecomparison}{All codes solve Maxwell's equations in its
  differential form (DE) under the quasistatic approximation. Note that
  \emg3d is a solver on its own, while the other codes implement third-package
  solvers such as \texttt{PETSc}, \texttt{MUMPS}, \texttt{FEniCS}
  \citep{CSE.15.Alnaes}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
  Method & FE & FIT & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & PEC & PEC & Neumann; Dirichlet & Dirichlet; Neumann \\
  Solver & \texttt{PETSc}; \texttt{MUMPS} & \emg3d & \texttt{FEniCS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

@@

>>>>

\tabl[btp]{codecomparison}{All codes solve Maxwell's equations in its
  differential form (DE) under the quasistatic approximation. Note that
  \emg3d is a solver on its own, while the other codes implement third-package
  solvers such as \texttt{PETSc}, \texttt{MUMPS}, or \texttt{PARDISO}
  \citep{FGCS.04.Schenk}.
  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}
  \imycom[DW]{PEC/PMC instead of Dirichlet/Neumann?}
}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FIT & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & Neumann; Dirichlet & PEC & PEC & Dirichlet; Neumann \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

\texttt{FEniCS} \citep{CSE.15.Alnaes}

@@

\paragraph{Comments Raphael} “\emph{Yes, cutting the layers has an influce at
  offsets greater distance X (see example \#2 thesis) - depending on the
  boundary mesh. I'm sure that's the reason. I could also add a version with a
  way larger horizontal layered earth extent, but this would require way more
  resources - unstructured meshes are just not competitive to regular grids for
  regular geopmetries in such cases as discussed before}“
